---
title: "Report_RData"
author: "MariyaGolchinpour"
date: "2022-11-24"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
Download the MAF files for the following TCGA projects ACC, SARC, BRCA using the TCGABiolinks
package in R.\
(a) Save all datasets as RData files in the separate folders and files.\
 for first part we get all ACC, SARC, BRCA data using the TCGABiolinks and save as RData.\
 
 
```{r}
library(maftools)
```
(b)Use the maftools package to plot three plots of your choice and save the figures (in PDF and
PNG) in a neat folder structure.\

for part b : load RData from part a and then plot different maftools plot.\
 
# oncoplot

load  ACC RData and the plot oncoplot

```{r load RData plot oncoplot}
name<- "ACC"
input_name_path=paste0("inputs/maf/",name,"/",name,"_maf.RData")
load(file.path(input_name_path), RData <- new.env() )
laml <- read.maf(maf = RData$maf)
oncoplot(maf = laml, top = 10)

```

## RainfallPlot

load BRCA RData and then plot rainfallPlot

```{r BRCA rainfallPlot}
name<- "BRCA"
input_name_path=paste0("inputs/maf/",name,"/",name,"_maf.RData")
load(file.path(input_name_path), RData <- new.env() )
laml <- read.maf(maf = RData$maf)
rainfallPlot(maf = laml, detectChangePoints = TRUE, pointSize = 0.4)

```

## SARC plotmafSummary

load SARC RData and then plot plotmafSummary

```{r SARC plotmafSummary}
name<- "SARC"
input_name_path=paste0("inputs/maf/",name,"/",name,"_maf.RData")
load(file.path(input_name_path), RData <- new.env() )
laml <- read.maf(maf = RData$maf)
plotmafSummary(maf = laml, rmOutlier = TRUE, addStat = 'median', dashboard = TRUE, titvRaw = FALSE)
 
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
